---
title: "Lecture 8 - Visualization 1"
output: git_document
---

# Re-install packages (bc I updated R version) and install ggrides and rnoaa packages

```{r}
install.packages(c("tidyverse", "knitr", "janitor", "broom", "here", "shiny", "readxl", "haven", "ggridges", "viridis", "skimr", "rvest", "httr", "flexdashboard", "devtools", "rmarkdown", "modelr"))
install.packages("rnoaa")

library(tidyverse)
library(ggridges)
library(rnoaa)
```

# import sample data and organize

```{r}
pulse_data = haven::read_sas("./Lecture 8 - Visualization 1/sample data/public_pulse_data.sas7bdat") 
janitor::clean_names()
pulse_data
```
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```

# Basic scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))

ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()

weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()

plot_weather = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) 

plot_weather + geom_point()

```

# Advanced Scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))

ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  geom_smooth(se = FALSE)

ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)

ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

# Learning Assessment: Write a code chain that starts with weather_df; focuses only on Central Park, converts temperatures to Fahrenheit, makes a scatterplot of min vs. max temperature, and overlays a linear regression line (using options in geom_smooth()).

```{r}

```

# Tips and Tricks

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_smooth(se = FALSE) 

ggplot(weather_df, aes(x = tmax, y = tmin)) + 
  geom_hex()
```

# Univariate Plots

```{r}
ggplot(weather_df, aes(x = tmax)) + 
  geom_histogram()

ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram(position = "dodge", binwidth = 2)

ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_density(alpha = .4, adjust = .5, color = "blue")

ggplot(weather_df, aes(x = name, y = tmax)) + geom_boxplot()

ggplot(weather_df, aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), color = "blue", alpha = .5) + 
  stat_summary(fun.y = median, geom = "point", color = "blue", size = 4)

ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```

# Learning Assessment: Make plots that compare precipitation across locations. Try a histogram, a density plot, a boxplot, a violin plot, and a ridgeplot; use aesthetic mappings to make your figure readable.

```{r}
```

# Saving and embedding Plots

```{r}
weather_plot = ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) 

ggsave("weather_plot.pdf", weather_plot, width = 8, height = 5)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```

# Learning Assessment: Set global options for your figure sizes in the “setup” code chunk and re-knit your document. What happens when you change fig.asp? What about out.width?

```{r}
```


